Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-04-03 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Update latex
add ng time avg plots, script and update latex

\begin{figure}[p]
  \centering
  \includegraphics[width=4.5in]{../Figures/Fig6}\\
  \includegraphics[width=4.5in]{../Figures/Fig7}\\
  \includegraphics[width=4.5in]{../Figures/Fig8}\\
  \caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
  \label{Temp}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p61m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p31m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p15m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0m_Reps_Avg}\\
	\caption[Plume temperatures along the centerline of the natural gas fueled burner]{Plume temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
	\label{TC_Plume_TWNG_comp}
\end{figure}

\begin{figure}[p]
	\centering
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p61m_Reps_Avg}\\
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p31m_Reps_Avg}\\
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p15m_Reps_Avg}\\
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0m_Reps_Avg}\\
	\caption[Wall Temperatures along the centerline of the natural gas fueled burner]{Wall Temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Surf_Cent_TWNG_comp}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p61m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p31m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p15m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0m_Reps_Avg}\\
	\caption[Wall Temperatures along the edge of the natural gas fueled burner]{Wall Temperatures along the right edge of the natural gas fueled burner, when facing the wall. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Surf_Edge_TWNG_comp}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p61m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p31m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p15m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0m_Reps_Avg}\\
	\caption[Backside wall Temperatures along the centerline of the natural gas fueled burner]{Backside wall Temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Back_Center_TWNG_comp}
\end{figure}

>>>>

\begin{figure}[p]
  \centering
  \includegraphics[width=3.5in]{../Figures/FHNG_TC_Plume_Avg}\\
  \includegraphics[width=3.5in]{../Figures/FHPUF_TC_Plume_Avg}\\
  \includegraphics[width=3.5in]{../Figures/FHGAS_TC_Plume_Avg}\\
  \caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
  \label{Temp}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=2.5in]{../Figures/TWNG01_TC_Plume_Avg}
	\includegraphics[width=2.5in]{../Figures/TWNG03_TC_Plume_Avg}\\
	\includegraphics[width=2.5in]{../Figures/TWNG05_TC_Plume_Avg}
	\includegraphics[width=2.5in]{../Figures/TWNG07_TC_Plume_Avg}\\
	\caption[Plume temperatures along the centerline of the natural gas fueled burner]{Plume temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
	\label{TC_Plume_TWNG_comp}
\end{figure}

\begin{figure}[ht!]
	\centering
		\includegraphics[width=2.5in]{../Figures/TWNG01_TC_Surface_Center_Avg}
		\includegraphics[width=2.5in]{../Figures/TWNG03_TC_Surface_Center_Avg}\\
		\includegraphics[width=2.5in]{../Figures/TWNG05_TC_Surface_Center_Avg}
		\includegraphics[width=2.5in]{../Figures/TWNG07_TC_Surface_Center_Avg}\\
	\caption[Wall Temperatures along the centerline of the natural gas fueled burner]{Wall Temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Surf_Cent_TWNG_comp}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=2.5in]{../Figures/TWNG01_TC_Surface_Offset_Avg}
	\includegraphics[width=2.5in]{../Figures/TWNG03_TC_Surface_Offset_Avg}\\
	\includegraphics[width=2.5in]{../Figures/TWNG05_TC_Surface_Offset_Avg}
	\includegraphics[width=2.5in]{../Figures/TWNG07_TC_Surface_Offset_Avg}\\
	\caption[Wall Temperatures along the edge of the natural gas fueled burner]{Wall Temperatures along the right edge of the natural gas fueled burner, when facing the wall. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Surf_Edge_TWNG_comp}
\end{figure}

\begin{figure}[ht!]
	\centering
	\includegraphics[width=2.5in]{../Figures/TWNG01_TC_Back_Center_Avg}
	\includegraphics[width=2.5in]{../Figures/TWNG03_TC_Back_Center_Avg}\\
	\includegraphics[width=2.5in]{../Figures/TWNG05_TC_Back_Center_Avg}
	\includegraphics[width=2.5in]{../Figures/TWNG07_TC_Back_Center_Avg}\\
	\caption[Backside wall Temperatures along the centerline of the natural gas fueled burner]{Backside wall Temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Back_Center_TWNG_comp}
\end{figure}
